---
title       : California schools as measured by standardized testing
subtitle    : https://dmaust.shinyapps.io/CaliforniaSchools/
author      : David Maust
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


# Every Child is Unique

When choosing a school for your child, there are many important
factors to consider

- Ability of your child.
- Your child's areas of interest.
- Your particular school district.

With my tool, users are able to view relevant test results for their particular district, for the grade level of interest, with their subject of interest.

--- &twocol w1:70% w2:30%

# Distribution of California Schools

*** =right

```{r echo=FALSE}
library(ggplot2)
load('/home/dmaust/git/CaliforniaSchools/school_data.Rda')
school_data_clean <- school_data[school_data$School.Code != 0,]
agg_data <- aggregate(
    cbind(
      as.numeric(Percentage.At.Or.Above.Proficient) * Students.with.Scores/100, 
      as.numeric(Students.with.Scores) 
      )  
        ~ School.Code + District.Code, school_data_clean, FUN=sum)
names(agg_data)[3] <- 'Proficient'
names(agg_data)[4] <- 'Students.with.Scores'
agg_data$Percent.Proficient = agg_data$Proficient * 100 / agg_data$Students.with.Scores
agg_data <- agg_data[agg_data$Students.with.Scores > 100,]

```
```{r warning=FALSE, echo=FALSE}
print(ggplot(agg_data, aes(x = Percent.Proficient)) + geom_histogram( binwidth=3))
```

*** =left
Here we can see the distribution of test scores through California schools. With this much variation, it is important to be informed when selecting a school for your child.

With the my application it is easy to detemine which are the high performing schools, and which are the low perfomers in your district.

---

# Dataset

Data is taken from the California Department of Education's website [1]. In it, there are data for `r length(unique(entity_data$District.Name))` different districts, containing `r length(unique(entity_data$School.Name))` schools. For these districts, `r sum(school_data_clean$Students.with.Scores)` test scores were recorded. For each of these, the level of proficiency is reported as: 
- Far Below Basic
- Below Basic
- Basic
- Proficient
- Advanced

With my application you are able to see the fraction of "Proficient" and "Advanced" scores achieved for each school in a given district, and you'll be able to see see it broken down by grade level and by subject.

[1] - <a href="http://star.cde.ca.gov/star2013/index.aspx">California STAR Program</a>

--- &twocol

# Tests Reported

You are able to see results broken down by grade levels, and for the following tests:
```{r echo=FALSE}
items <- lapply(tests$Test.Name, FUN=function(test){paste("<li style=\"font-size: 12pt;\"> ",test,"</li>")})
```
*** =left
<ul>
`r paste(items[1:16], collapse='')`.
</ul>
*** =right
<ul>
`r paste(items[17:32], collapse='')`.
</ul>